\thetitle

### 2021-03-03 writing/conclusion.tex
pass over section 11
rw and conclusion: small edits

The paper provides the first insight into the measurable value of blame in the
gradually typed world. In an implicit manner researchers and language designers
have answered this question one way or another, but without evidence. Now they
may use the evaluation method of this paper to rationalize their answers.  The
work of~\citet{tgpk-dls-2018} suggests that, by intuition, programmers prefer
the run-time checking of Natural over other soundness methods. But, just because
a random set of programmers expresses this view does not mean that blame
assignment adds value. At this point, it is clear that, in some circumstances,
it does and in others, the answer remains murky.

>>>>

The paper provides the first insight into the measurable value of blame in the
gradually typed world. In an implicit manner researchers and language designers
have answered this question one way or another, but without evidence. Now they
may use the evaluation method of this paper to rationalize their answers.  The
work of~\citet{tgpk-dls-2018} suggests that, by intuition, programmers prefer
the run time checking of Natural over other soundness methods. But just because
a random set of programmers expresses this view does not mean that blame
assignment adds value. At this point it is clear that in some circumstances
it does, and in others the answer remains murky.

### 2021-03-03 writing/related.tex
rw and conclusion: small edits

\citet{lksfd-popl-2020}'s human-out-of-the-loop empirical analysis of blame for
higher-order contracts in the inspiration for this paper.  While they do not
spell out the notion of the rational programmer, they present the basic
ingredients of the technique.

Technically, this work and~\citet{lksfd-popl-2020}'s differ in many ways. The
experiment presented here concerns three different modes of gradual typing,
theirs a single notion of contract checking.  It also contributes the idea of
creating three comparable rational programmers (with several modes). The
type-level mutators represent another technical contribution of the work
presented here; as explained in section~\ref{sec:mutate}, almost none
of~\citet{lksfd-popl-2020}'s mutators is useful at the level of type mistakes.

>>>>

\citet{lksfd-popl-2020}'s human-out-of-the-loop empirical analysis of blame for
higher-order contracts is the inspiration for this paper.  While they do not
spell out the notion of the rational programmer, they present the basic
ingredients of the technique.

At a technical level, this work and~\citet{lksfd-popl-2020}'s differ in
many ways. The experiment presented here concerns three different modes of
gradual typing, theirs a single notion of contract checking.  It also
contributes the idea of creating three comparable rational programmers
(with several modes). Thus the method of this paper answers whether blame
adds value to a gradual type system and what gradual type system it
benefits the most; while~\citet{lksfd-popl-2020} only establish a
systematic relation between blame for contracts and behavioral bugs. The
type-level mutators represent another technical contribution of the work
presented here; as explained in section~\ref{sec:mutate}, almost none
of~\citet{lksfd-popl-2020}'s mutators is useful at the level of type
mistakes.
